Transcriptomic Analysis for Prognostic Value in Head and Neck Squamous Cell Carcinoma

### 2021-07-06 Supplementary_figures.tex
Updates from Overleaf

% mark in blue or red
\usepackage{xcolor}
%\usepackage[table,xcdraw]{xcolor}
%\newenvironment{MyColorPar}[1]{%
%    \leavevmode\color{#1}\ignorespaces%
%}{%
%}%

@@

\section{STables}
%\underline{Supplementary figure legends}\\[1cm]
%ST1
%Supplementary Table \ref{table:table1}\\
%GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of high risk and low risk groups, which is derived from cumulative P-value plots). The poor prognostic genes are marked as red; the better prognostic genes are marked as green.

@@

\resizebox{\linewidth}{!}{

@@

\begin{tabularx}{\textwidth}{|l|p{3.5cm}|l|l|l|l|l|l|c|} % *** capital X or p{2cm}

@@

\multicolumn{1}{|c|}{\multirow{2}{*}{Gene ID}} & \multicolumn{1}{c|}{\multirow{2}{*}{Gene Description}}     & \multicolumn{2}{c|}{Kaplan-Meier survival}                                                                                   & \multicolumn{2}{c|}{Univariate~}                                                        & \multicolumn{2}{c|}{Multivariate}                                                       & \multirow{2}{*}{Remark}                     \\ 

@@

\multicolumn{1}{|c|}{}                         & \multicolumn{1}{c|}{}                                      & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}FDR \\\textit{P} value\end{tabular}}               & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}Bonferroni \\\textit{P} value\end{tabular}} & \multicolumn{1}{c|}{HR*}                   & 95\% CI                                    & HR*                                        & 95\% CI                                    &                                             \\ 
DKK1                                           & dickkopf WNT signaling pathway inhibitor 1                 & \num{8.9e-8}                               & 0.001                                                                           & 2.266                                      & 1.666-3.082                                & 2.135                                      & 1.559-2.924                                &                                           \\ 
CAMK2N1                                        & calcium/calmodulin-dependent protein kinase II inhibitor 1 & \num{2.9e-7}                               & 0.002                                                                           & 2.101                                      & 1.572-2.809                                & 2.007                                      & 1.490-2.704                                &                                           \\ %\checkmark
STC2                                           & stanniocalcin 2                                            & \num{6.5e-7}                               & 0.004                                                                           & 2.147                                      & 1.578-2.921                                & 2.075                                      & 1.515-2.843                                &                                           \\ 
PGK1                                           & phosphoglycerate kinase 1                                  & \num{9.1e-7}                               & 0.006                                                                           & 2.127                                      & 1.563-2.895                                & 2.046                                      & 1.498-2.795                                &                                           \\ %\checkmark
SURF4                                          & surfeit 4                                                  & \num{9.6e-7}                               & 0.006                                                                           & 2.055                                      & 1.531-2.757                                & 2.089                                      & 1.543-2.829                                &                                          \\ %\checkmark  
USP10                                          & ubiquitin specific peptidase 10                            & \num{1.7e-6}                               & 0.012                                                                           & 2.083                                      & 1.532-2.834                                & 2.119                                      & 1.551-2.895                                &                                          \\ %\checkmark
NDFIP1                                         & Nedd4 family interacting protein 1                         & \num{2.6e-6}                               & 0.017                                                                           & 2.031                                      & 1.502-2.746                                & 2.027                                      & 1.483-2.771                                &                                           \\ %\checkmark 
FOXA2                                          & forkhead box A2                                            & \num{2.7e-6}                               & 0.018                                                                           & 1.976                                      & 1.479-2.640                                & 1.914                                      & 1.426-2.569                                &                                         \\ %\checkmark  
STIP1                                          & stress-induced-phosphoprotein 1                            & \num{4.3e-6}                              & 0.029                                                                           & 1.958                                      & 1.463-2.621                                & 1.957                                      & 1.451-2.640                                &                                           \\ 
DKC1                                           & dyskeratosis congenita 1, dyskerin                         & \num{6.3e-6}                               & 0.042                                                                           & 2.046                                      & 1.490-2.808                                & 1.837                                      & 1.332-2.534                                &                                           \\ 
\multicolumn{1}{|l!{\color{black}\vrule}}{}    & \multicolumn{1}{l!{\color{black}\vrule}}{}                 & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{}                                      & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{}  \\ 
\arrayrulecolor{black}\hline
\multicolumn{9}{|l!{\color{black}\vrule}}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~~\\~Kaplan-Meier Bonferroni-adjusted \textit{P} $< 0.05 $~\\~Cox's univariate and multivariate$ HR > 1.5$ \end{tabular}}                                                                                                                                                                                                                                                              \\ 
\multicolumn{9}{|l!{\color{black}\vrule}}{* Cox's model: \textit{P} $< 0.001$ }                                                                                                                                                                                                                                                                                                                                                                                                  \\ 
%\multicolumn{9}{|l!{\color{black}\vrule}}{Remark: \checkmark validated by GSE2837}                i                                                                                                                                                                                                                                                                                                                                             \\
\end{tabularx}
} % resizebox end
\label{table:table1}

@@

\begin{tabular}{|l|l|l|l|l|l|l|l|c|} 

@@

\multicolumn{1}{|c|}{\multirow{2}{*}{Gene ID}} & \multicolumn{1}{c|}{\multirow{2}{*}{Gene Description}} & \multicolumn{2}{l|}{Kaplan-Meier survival}                                                                                                                                                & \multicolumn{2}{c|}{Univariate~}                                                                        & \multicolumn{2}{c|}{Multivariate}                                                                       & \multicolumn{1}{l|}{\multirow{2}{*}{Remark}}  \\ 
\multicolumn{1}{|c|}{}                         & \multicolumn{1}{c|}{}                                  & \multicolumn{1}{c!{\color{black}\vrule}}{\begin{tabular}[c]{@{}c@{}}FDR\\~\textit{P} value\end{tabular}}                                  & \multicolumn{1}{c!{\color{black}\vrule}}{\begin{tabular}[c]{@{}c@{}}Bonferroni\\~\textit{P} value\end{tabular}} & \multicolumn{1}{c!{\color{black}\vrule}}{HR*}   & \multicolumn{1}{c!{\color{black}\vrule}}{95\% CI}     & \multicolumn{1}{c!{\color{black}\vrule}}{HR*}   & \multicolumn{1}{c!{\color{black}\vrule}}{95\% CI}     & \multicolumn{1}{l|}{}                         \\ 
\cline{1-2}\arrayrulecolor{black}\cline{3-8}\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{9-9}
ZNF557                                         & zinc finger protein 557                                & \multicolumn{1}{l!{\color{black}\vrule}}{\num{8.6e-8}} & \multicolumn{1}{l!{\color{black}\vrule}}{0.001}                                                      & \multicolumn{1}{l!{\color{black}\vrule}}{0.465} & \multicolumn{1}{l!{\color{black}\vrule}}{0.348-0.619} & \multicolumn{1}{l!{\color{black}\vrule}}{0.499} & \multicolumn{1}{l!{\color{black}\vrule}}{0.372-0.669} &                                              \\ 
\cline{1-2}\arrayrulecolor{black}\cline{3-8}\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{9-9}
ZNF266                                         & zinc finger protein 266                                & \num{2.2e-7}                                           & 0.001                                                                                                & 0.474                                           & 0.355-0.632                                           & 0.453                                           & 0.338-0.607                                           &                                              \\ 

@@

IL19                                           & interleukin 19                                         & \num{3.7e-7}               & 0.002                                                                                                & 0.472                                           & 0.351-0.635                                           & 0.459                                           & 0.340-0.619                                           &                                             \\ %\checkmark

@@

MYO1H                                          & myosin 1H                                              & \num{3.8e-7}               & 0.003                                                                                                & 0.468                                           & 0.347-0.632                                           & 0.467                                           & 0.344-0.634                                           &                                              \\ 
FCGBP                                          & Fc fragment of IgG binding protein                     & \num{1.2e-6}               & 0.008                                                                                                & 0.484                                           & 0.359-0.653                                           & 0.496                                           & 0.366-0.674                                           &                                             \\ %\checkmark

@@

EVPLL                                          & envoplakin-like protein                                & \num{2.0e-6}                                           & 0.013                                                                                                & 0.490                                           & 0.363-0.661                                           & 0.494                                           & 0.364-0.672                                           &                                              \\ 

@@

PNMA5                                          & paraneoplastic antigen like 5                          & \num{2.6e-6}                                           & 0.017                                                                                                & 0.499                                           & 0.371-0.671                                           & 0.481                                           & 0.357-0.650                                           &                                              \\ 

@@

IQCN                           & \num{3.1e-6}                                           & 0.020                                                                                                & 0.500                                           & 0.371-0.673                                           & 0.483                                           & 0.356-0.654                                           &                                              \\ %\checkmark

@@

NPB                                            & neuropeptide B                                         & \num{4.0e-6}                                           & 0.027                                                                                                & 0.460                                           & 0.328-0.646                                           & 0.457                                           & 0.324-0.646                                           &                                              \\ %\checkmark

@@

   0.364-0.667 &  \\  % \checkmark \multicolumn{2}{l|} {

@@

\multicolumn{9}{|l|}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~\\~Kaplan-Meier Bonferroni-adjusted \textit{P} value \textless{} 0.05~\\~Cox's univariate and multivariate HR \textless{} 0.6\\

@@

* Cox's model: \textit{P} $< 0.001$ \\
%}                                                                                                                                                                                                                                                                                                                                                                                                  \\ 

@@

~\end{tabular}}                                                                                                                                                                                                                 \\

@@

\section{SFigures}
%\underline{Supplementary figure legends}\\[1cm]
%S1
Supplementary figure \ref{fig:pvaluePlot_NDFIP1}:\\
The gene NDFIP1, one of our 20 preliminary candidates, has a \textit{P} value (around $0.05$) at 50\% quantile cutoff, achieving a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff.% (please see supplementary Figure S1).
After the FDR correction, NDFIP1 still has \textit{P} value of \num[round-precision=3, round-mode=figures,
scientific-notation=true]{0.0001074233}.
However, NDFIP1 could not pass the validation by using GSE65858 cohort.

>>>>

% mark in blue or red
\usepackage{xcolor}
\definecolor{asparagus}{rgb}{0.53, 0.66, 0.42}

%\usepackage[table,xcdraw]{xcolor}
%\newenvironment{MyColorPar}[1]{%
%    \leavevmode\color{#1}\ignorespaces%
%}{%
%}%

@@

%\section{STables}
%\underline{Supplementary figure legends}\\[1cm]
%ST1
%Supplementary Table \ref{table:table1}\\
%GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of high risk and low risk groups, which is derived from cumulative P-value plots). The poor prognostic genes are marked as red; the better prognostic genes are marked as green.

@@

@@

\begin{tabularx}{\textwidth}{|l|p{3.5cm}|l|l|l|l|l|l|} % *** capital X or p{2cm}

@@

\cline{1-8}
\multicolumn{1}{|c|}{\multirow{2}{*}{Gene ID}} & \multicolumn{1}{c|}{\multirow{2}{*}{Gene Description}}     & \multicolumn{2}{c|}{Kaplan-Meier survival}                                                                                   & \multicolumn{2}{c|}{Univariate~}                                                        & \multicolumn{2}{c|}{Multivariate} \\

@@

\multicolumn{1}{|c|}{}                         & \multicolumn{1}{c|}{}                                      & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}FDR \\ \textit{P} value\end{tabular}}               & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}Bonferroni \\\textit{P} value\end{tabular}} & \multicolumn{1}{c|}{HR*}                   & 95\% CI                                    & HR*                                        & 95\% CI   \\\cline{1-8}
DKK1                                           & dickkopf WNT signaling pathway inhibitor 1                 & \num{3.8e-6}                               & 0.001                                                                           & 2.266                                      & 1.666-3.082                                & 2.135                                      & 1.559-2.924     \\                          % &                                           \\ 
\cline{1-8}
CAMK2N1                                        & calcium/calmodulin-dependent protein kinase II inhibitor 1 & \num{1.5e-5}                               & 0.002                                                                           & 2.101                                      & 1.572-2.809                                & 2.007                                      & 1.490-2.704  \\                            % &                                           \\ %\checkmark
\cline{1-8}
STC2                                           & stanniocalcin 2                                            & \num{1.5e-5}                               & 0.004                                                                           & 2.147                                      & 1.578-2.921                                & 2.075                                      & 1.515-2.843                             \\%   &                                           \\ 
\cline{1-8}
PGK1                                           & phosphoglycerate kinase 1                                  & \num{2.4e-5}                               & 0.006                                                                           & 2.127                                      & 1.563-2.895                                & 2.046                                      & 1.498-2.795                              \\%    &                                           \\ %\checkmark
\cline{1-8}
SURF4                                          & surfeit 4                                                  & \num{6.2e-5}                               & 0.006                                                                           & 2.055                                      & 1.531-2.757                                & 2.089                                      & 1.543-2.829                               \\%   &                                          \\ %\checkmark  
\cline{1-8}
USP10                                          & ubiquitin specific peptidase 10                            & \num{7.9e-5}                               & 0.012                                                                           & 2.083                                      & 1.532-2.834                                & 2.119                                      & 1.551-2.895                              \\%    &                                          \\ %\checkmark
\cline{1-8}
NDFIP1                                         & Nedd4 family interacting protein 1                         & \num{1.1e-4}                               & 0.017                                                                           & 2.031                                      & 1.502-2.746                                & 2.027                                      & 1.483-2.771                               \\%   &                                           \\ %\checkmark 
\cline{1-8}
FOXA2                                          & forkhead box A2                                            & \num{1.6e-4}                               & 0.018                                                                           & 1.976                                      & 1.479-2.640                                & 1.914                                      & 1.426-2.569                               \\%   &                                         \\ %\checkmark  
\cline{1-8}
STIP1                                          & stress-induced-phosphoprotein 1                            & \num{1.8e-4}                              & 0.029                                                                           & 1.958                                      & 1.463-2.621                                & 1.957                                      & 1.451-2.640                               \\%   &                                           \\ 
\cline{1-8}
DKC1                                           & dyskeratosis congenita 1, dyskerin                         & \num{2.8e-4}                               & 0.042                                                                           & 2.046                                      & 1.490-2.808                                & 1.837                                      & 1.332-2.534                               \\%   &                                          \\ 
\cline{1-8}
%\multicolumn{1}{|l!{\color{black}\vrule}}{}    & \multicolumn{1}{l!{\color{black}\vrule}}{}                 & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{}                                      & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{}  \\ 
%\arrayrulecolor{black}\hline

\multicolumn{8}{|l|}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~~\\~Kaplan-Meier Bonferroni-adjusted \textit{P} $< 0.05 $~\\~Cox's univariate and multivariate $HR > 1.5$~\\~(* Cox's model: \textit{P} $< 0.001$)\\ \end{tabular}}   \\ 
%\cline{1-8}
%\multicolumn{8}{|l|}{Selection criteria:~\\~Kaplan-Meier Bonferroni-adjusted \textit{P} $< 0.05 $~\\~Cox's univariate and multivariate $HR > 1.5$~\\~* Cox's model: \textit{P} $< 0.001$}   \\ 
\cline{1-8}
%\multicolumn{9}{|l!{\color{black}\vrule}}{Remark: \checkmark validated by GSE2837}                i                                                                                                                                                                                                                                                                                                                                             \\
%\hline
\end{tabularx}%
} % resizebox end
\arrayrulecolor{black}
\label{table:table1}

@@

\begin{tabular}{|l|l|l|l|l|l|l|l|} 
\cline{1-8}
\multicolumn{1}{|c|}{\multirow{2}{*}{Gene ID}} & \multicolumn{1}{c|}{\multirow{2}{*}{Gene Description}} & \multicolumn{2}{l|}{Kaplan-Meier survival}                                                                                                                                                & \multicolumn{2}{c|}{Univariate~}                                                                        & \multicolumn{2}{c|}{Multivariate}                                                                    \\%   & \multicolumn{1}{l|}{\multirow{2}{*}{Remark}}  \\ 
\multicolumn{1}{|c|}{}                         & \multicolumn{1}{c|}{}                                  & \multicolumn{1}{c!{\color{black}\vrule}}{\begin{tabular}[c]{@{}c@{}}FDR\\~\textit{P} value\end{tabular}}                                  & \multicolumn{1}{c!{\color{black}\vrule}}{\begin{tabular}[c]{@{}c@{}}Bonferroni\\~\textit{P} value\end{tabular}} & \multicolumn{1}{c!{\color{black}\vrule}}{HR*}   & \multicolumn{1}{c!{\color{black}\vrule}}{95\% CI}     & \multicolumn{1}{c!{\color{black}\vrule}}{HR*}   & \multicolumn{1}{c!{\color{black}\vrule}}{95\% CI}    \\%   & \multicolumn{1}{l|}{}                         \\ 
\cline{1-2}\arrayrulecolor{black}\cline{3-8}%\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{9-9}
ZNF557                                         & zinc finger protein 557                                & \multicolumn{1}{l!{\color{black}\vrule}}{\num{4.7e-6}} & \multicolumn{1}{l!{\color{black}\vrule}}{0.001}                                                      & \multicolumn{1}{l!{\color{black}\vrule}}{0.465} & \multicolumn{1}{l!{\color{black}\vrule}}{0.348-0.619} & \multicolumn{1}{l!{\color{black}\vrule}}{0.499} & \multicolumn{1}{l!{\color{black}\vrule}}{0.372-0.669}                                              \\ 
\cline{1-2}\arrayrulecolor{black}\cline{3-8}%\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{9-9}
ZNF266                                         & zinc finger protein 266                                & \num{5.2e-6}                                           & 0.001                                                                                                & 0.474                                           & 0.355-0.632                                           & 0.453                                           & 0.338-0.607                                                                                       \\ 

@@

IL19                                           & interleukin 19                                         & \num{6.5e-6}               & 0.002                                                                                                & 0.472                                           & 0.351-0.635                                           & 0.459                                           & 0.340-0.619                                          \\%   &                                             \\ %\checkmark

@@

MYO1H                                          & myosin 1H                                              & \num{1.4e-5}               & 0.003                                                                                                & 0.468                                           & 0.347-0.632                                           & 0.467                                           & 0.344-0.634                                          \\%   &                                              \\ 

@@

FCGBP                                          & Fc fragment of IgG binding protein                     & \num{4.8e-5}               & 0.008                                                                                                & 0.484                                           & 0.359-0.653                                           & 0.496                                           & 0.366-0.674                                        \\%     &                                             \\ %\checkmark

@@

EVPLL                                          & envoplakin-like protein                                & \num{7.5e-5}                                           & 0.013                                                                                                & 0.490                                           & 0.363-0.661                                           & 0.494                                           & 0.364-0.672                                            \\% &                                              \\ 

@@

PNMA5                                          & paraneoplastic antigen like 5                          & \num{3.0e-4}                                           & 0.017                                                                                                & 0.499                                           & 0.371-0.671                                           & 0.481                                           & 0.357-0.650                                            \\% &                                              \\ 

@@

IQCN            & IQ motif containing N               & \num{1.5e-4}                                           & 0.020                                                                                                & 0.500                                           & 0.371-0.673                                           & 0.483                                           & 0.356-0.654                  \\%                           &                                              \\ %\checkmark

@@

NPB                                            & neuropeptide B                                         & \num{2.6e-4}                                           & 0.027                                                                                                & 0.460                                           & 0.328-0.646                                           & 0.457                                           & 0.324-0.646                                            \\% &                                              \\ %\checkmark

@@

   0.364-0.667  \\%  &  \\  % \checkmark \multicolumn{2}{l|} {

@@

\multicolumn{8}{|l|}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~\\~Kaplan-Meier Bonferroni-adjusted \textit{P} value \textless{} 0.05~\\~Cox's univariate and multivariate HR \textless{} 0.6\\

@@

(* Cox's model: \textit{P} $< 0.001$) \\
%}                                                                              

@@

\end{tabular}}                                                                   \\ \hline

@@

%\section{SFigures}
%\underline{Supplementary figure legends}\\[1cm]
%S1
Supplementary figure \ref{fig:pvaluePlot_NDFIP1}:\\
The gene NDFIP1, one of our 20 preliminary candidates, has a \textit{P} value (around $0.05$) at 50\% quantile cutoff, achieving a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff.% (please see supplementary Figure S1).
After the FDR correction, NDFIP1 still has \textit{P} value of \num[round-precision=3, round-mode=figures,
scientific-notation=true]{0.0001074233}.
However, NDFIP1 could not pass the validation by using GSE65858 cohort.
